\chapter{A Brain-Inspired Algorithm}
\label{chp_htm}
\textit{Hierarchical Temporal Memory} (HTM) is a theory of how the human neocortex processes information, be it auditory, visual, motor, or somatosensory signals, developed by Jeff Hawkins \cite{Hawkins:2004:INT:993636}. It was long known that the neocortex looked remarkably similar in all different regions, this made anatomists to focus on the minuscule differences between the cortical regions to find the answer how they worked. However, in 1978, a neuroscientist by the name of Vernon B. Mountcaslte stopped focusing on the differences and saw that it was the similarities of the cortical regions that mattered. He came up with a theory of a single algorithm by which the neocortex processes information. The small differences that the anatomists found, was only because of the different types of signals that where being processed, not a difference in the algorithm itself \cite{Hawkins:2004:INT:993636}. With this idea of a single algorithm, Jeff Hawkins started a company called Numenta, with the intention of figuring out this algorithm. Numenta has since published an open-source project named Numenta Platform for Intelligent Computing, or NuPIC, which is an implementation of the HTM theory. 

In this chapter, we will start by introducing the HTM neuron. Then, we proceed to explain the way information is represented in an HTM network. Finally, we explain the sequence learning algorithm, called temporal memory.


\input{background/HTM/HTMNeuron.tex}


\input{background/HTM/SDR.tex}


\input{background/HTM/TM.tex}