\chapter{The Neuroscience of the Neocortex}
\label{chp_neocortex}
This is a complementary chapter to \textit{''A Brain-Inspired Algorithm''}. We will go through some of the neuroscience of the \textit{new cerebral cortex} (neocortex), that the \textit{Hierarchical Temporal Memory} (HTM) theory is biologically derived from. We being by introducing the neocortex of the mammalian brain and why it is believed to be the part of the brain where intelligence resides. Then, the topology of the neocortex is presented, where we will go through the structure of each layer. Next, we describe the columnar organisation of the neocortex, first coined by Vernon B. Mountcastle, which is one of the main inspirations in HTM theory. We then continue to describe the neural circuitry of these cortical columns. Finally, we introduce the pyramidal neuron, which is the most frequently occurring type of neuron that resides in the neocortex. The HTM neuron is modelled on the pyramidal neuron's functionality and the active processing properties of its dendrites. 


\input{appendix/neuroscience/neocortex.tex}

\input{appendix/neuroscience/pyramidal.tex}

\section{Summary}
To summaries, HTM theory is derived from properties of the neocortex and the ideas of Vernon B. Mountcastle's single cortical algorithm for information processing. This chapter aimed to familiarise the reader with the structure and functionality of neocortex. First, a gentle introduction to the neocortex was given. Then, we proceeded to the topology and the structure of the individual layers. Next, cortical columns and the neural circuitry was presented, which HTM theory tries to reverse engineer to some extent. Finally, we presented the pyramidal neuron and the functionality of the dendrites. As this is the most abundant neuron in the neocortex, and the inspiration of the HTM neuron's functionality.





%To achieve true machine intelligence one must first be able to understand the information processing that occurs in the brain. Some AI researchers have discarded the idea of this principle with the argument that neither planes nor cars function in the same way as their biological counterparts \cite{Hawkins:2004:INT:993636}. However, intelligence should be defined as the methodology by which an autonomous agent is able to learn in the world \cite{Intelligence}. This means that intelligence resides in the inner workings of the brain and is not equivalent to behaviour. With this definition of intelligence; current state-of-the-art AI agents that can outperform humans in some specific tasks, such as image classification or Go, cannot be seen as intelligent. 



%Geoffrey Hinton, who is hailed as one of the godfathers of Deep Learning is ''deeply suspicious'' of the learning algorithm of Artificial Neural Networks called Back-Propagation, and encourages graduates to scrap this idea and explore new possibilities of learning for neural networks \cite{Hinton}.

%The goal of AI research is to create a Artificial General Intelligence that is on par or surpasses human intelligence. But what makes the human brain so special? It is the size of the \textit{new cerebral cortex} (neocortex) \cite{Neocortex}.